---
title: <span style="color:crimson">*Twitter*</span>
author: "Author: Bareket Karif"
date: "Date: 11 באפריל 2016"
output: html_document
---

___ 

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 200)
```

### <span style="color:darkorange">*Date Description:*</span>  
in this part I decided to look for twitts which include the words "read book" - I will use with twitteR.  
  
  
___

### <span style="color:darkorange">*Data Example - First data record:*</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
# Getting data from Twitter API

require(twitteR)
#require(jsonlite)
library(wordcloud)
require(tm)

consumer_key <- 'eoSG1kjNRB92J7QIiHN90NKPP'
consumer_secret <- 'pKdUaUnA7q40ut8ggwMcI7lazYJwlAiFcQOjAZbaiBQbwwAybj'
access_token <- '719470966779285504-pDCL4vnTJnay1Cwg1qXEuAwfzEwxHsL'
access_secret <- 'OwUCdiuOpxIFjwCh7vjmAUbPvm6iMjzoAPssn1v7hNqxd'

sig <- twitteR::setup_twitter_oauth(consumer_key,consumer_secret,access_token,access_secret)

file_book<-"book.R"
if(!file.exists(file_book)){
  book_tmp <- searchTwitter("#read books", n = 500)
  save(book_tmp, file=file_book, compress=TRUE)
} else
    load(file_book)

head(book_tmp)

# Get the Date
dateAPI <- date()
dateAPI

first_data_record <- twListToDF(book_tmp)
```
  
  
___
  
### <span style="color:darkorange">*Analysis of the data by various criteria*</span>  

#### The graph describe the **"wordCloud"** of the most common words
```{r twitteR, echo=FALSE, include= TRUE, warning=FALSE}
# get tweets with relevant data
Booktweets <- searchTwitter('#read books', n = 500, lang = 'en', resultType = "recent")

#save text
Book_text <- sapply(Booktweets, function(x) x$getText())

#create corpus
Book_text <- Corpus(VectorSource(Book_text))

#clean up
Book_text_corpus <- tm_map(Book_text, removePunctuation)
Book_text_corpus <- tm_map(Book_text_corpus, removeWords, stopwords("english"))
Book_text_corpus <- tm_map(Book_text_corpus, removeNumbers)
Book_text_corpus <- tm_map(Book_text_corpus, stripWhitespace)

#making a wordcloud
wordcloud(Book_text_corpus, random.order = F, max.words = 85, scale = c(5, 0.9), colors = brewer.pal(8, "Dark2"))
```

This graph shows the most common words in the wordCloud of "read book" is: book, read, the, this, books, best, now, bookworm, buy, kindle, amazon.  
  
  
___  

---
#### The graph describe how many twitts from the twitts are **retwitted**

```{r, echo=FALSE, include= TRUE, warning=FALSE}
# Pie Chart from data frame with Appended Sample Sizes
scraping_tweets <- twListToDF(Booktweets)
retweetTmp <- table(scraping_tweets$isRetweet)
boolean<-c('No','Yes')
lbls <- paste(boolean, "\n", retweetTmp, sep="")
pie(retweetTmp, labels = lbls, main="retwitted or not?",col=c('steelblue','violet'))  
```


This graph shows the distribution of the original tweets and repeated almost the same.
This suggests that when there is a tweet about a great story that many people connect to it, the above tweet will be published again and again.  
  
  
  
___  
  
#### The graph describe the count of **screenName** in the twitts

```{r, echo=FALSE, include= TRUE, warning=FALSE}
# Define the cars vector with 5 values
count <- table(scraping_tweets$screenName)

# Graph cars using blue points overlayed by a line 
plot(count , type="o", col="steelblue")

# Create a title with a red, bold/italic font
title(main="count of screenName in the twitts", col.main="black", font.main=4)
```


This graph show that the most common screenName is **chicklitplus** - it's contains book reviews authors interviews etc'.  
  
  
  
  
___
  
  
### <span style="color:darkorange">*Summary of Conclusions and Recommendations for Further Research*</span>  

In conclusion, this report shows that the private lenders have common attributes, such as retwitted about books.  
  
  
My recommendation for further research, is to use the information collected in this report, and examine the likelihood that any twitts about a specific book twitts later on other books by the same author. 


